Analyzing Trends on the Characteristics of Notable People on Wikipedia

### 2024-12-14 paper/paper.qmd
slightly updates paper, adds .gitignore

---
title: "Analyzing Trends on the Characteristics of Notable People on Wikipedia"
subtitle: "an Individuals Time Period and Occupation Strongly Associated with Prominence"
author: 
  - Parth Samant
thanks: "Code and data are available at: [https://github.com/samantparth/Wikipedia-Historical-Prominence-Trends](https://github.com/samantparth/Wikipedia-Historical-Prominence-Trends)."
date: today
date-format: long
abstract: "Wikipedia is an online encyclopedia that contains information on millions of diverse subjects, arguably serving as a repository for human knowledge. In this paper, I analyzed a dataset of notable people on Wikipedia from 3500 BCE to 2018 AD to identify whether certain characteristics (such as age and gender) were correlated with prominence. The analysis found that occupation and time period were most strongly associated with prominence, with subregion and gender being less significant. This highlights how prominence between already notable people selects for different characteristics."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---

@@

Wikipedia is an online encyclopedia has been one of the most popular references of information globally. Containing milllions of articles on the platform, and thus acting somewhat as an archive for human information. This encyclopedia provides information on a diverse range of topics from history to entertainment.

Within this vast encyclopedia, there is also a collection of biographical information on "notable people" who have ever lived in the past few thousand years. Thus, one research study [@notablepeople] compiled a dataset of notable people on Wikipedia from 3500 BCE to 2018.

@@

The findings of this paper showed that an individuals time period and occupation/field have a large effect on an individuals prominence. Those who were born in earlier time periods (such as before 500 BCE) were associated large increases in prominence. Additionally, those known for being part of a noble class, an important family, or for creative endeavors that shape culture (such as musicians, actors, or painters) also tend to have higher overall prominence.

Subregion was somewhat associated with prominence, but with a large amount of variability. Notable individuals from Eastern Asia tend to have high levels of prominence, whereas those from Central America and Southern Africa have less.

This paper also found that within those who are already prominent, gender tends to have a somewhat insignificant effect.

>>>>

---
title: "Analyzing Trends on the Characteristics of Notable People on Wikipedia"
subtitle: "Time Period and Occupation Strongly Associated with Individual Prominence"
author: 
  - Parth Samant
thanks: "Code and data are available at: [https://github.com/samantparth/Wikipedia-Historical-Prominence-Trends](https://github.com/samantparth/Wikipedia-Historical-Prominence-Trends)."
date: today
date-format: long
abstract: "Wikipedia is an online encyclopedia that contains information on millions of diverse subjects, arguably serving as a repository for human knowledge. In this paper, I analyzed a dataset of notable people on Wikipedia from 3500 BCE to 2018 AD to identify whether certain characteristics (such as age and gender) were correlated with prominence. The analysis found that occupation and time period were most strongly associated with prominence, with subregion and gender being less significant. This highlights how prominence between already notable people selects for different characteristics."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---

@@

Wikipedia is an online encyclopedia has been one of the most popular references of information globally. Containing milllions of articles on the platform, and thus acting somewhat as an archive for human information. This encyclopedia provides information on a diverse range of topics from history to entertainment. Within this vast encyclopedia, there is also a collection of biographical information on "notable people" who have ever lived in the past few thousand years. Thus, one research study [@notablepeople] compiled a dataset of notable people on Wikipedia from 3500 BCE to 2018.

@@

The findings of this paper showed that an individuals time period and occupation/field have a large effect on an individuals prominence. Those who were born in earlier time periods (such as before 500 BCE) were associated large increases in prominence. Additionally, those known for being part of a noble class, an important family, or for creative endeavors that shape culture (such as musicians, actors, or painters) also tend to have higher overall prominence.Subregion was somewhat associated with prominence, but with a large amount of variability. Notable individuals from Eastern Asia tend to have high levels of prominence, whereas those from Central America and Southern Africa have less. It was also found that within those who are already prominent, gender tends to have a somewhat insignificant effect.
